Concurrent Programming in Harmony

### 2021-11-15 book/paper.tex
Some more minor updates to the book

\index{ring buffer}%
A \emph{bounded buffer} (aka \emph{ring buffer}) is
a queue with the usual \texttt{put/get} interface,
but implemented using a circular buffer
\index{circular buffer}%
of a certain length and two pointers:
the \emph{tail} points where new items are enqueued and the \emph{head}
points where items are dequeued.
If the buffer is full, the enqueuer must wait; if the buffer is empty, the
dequeuer must wait.
\autoref{fig:boundedbuffer} specifies a bounded buffer.
Coming up with a good implementation is known as the
``Producer/Consumer Problem'' and was
proposed by Dijkstra~\cite{EWD329}.
Multiple producers and multiple consumers may all share
the same bounded buffer.

>>>>

A \emph{bounded buffer} is
a queue with the usual \texttt{put/get} interface,
but implemented using a buffer
of a certain maximum length.
If the buffer is full, the enqueuer must wait; if the buffer is empty, the
dequeuer must wait.
\autoref{fig:boundedbuffer} specifies a bounded buffer.
It is similar to the implementation in \autoref{fig:queues}(b) but adds
checking for bounds.
Coming up with a good implementation is known as the
``Producer/Consumer Problem'' and was
proposed by Dijkstra~\cite{EWD329}.
Multiple producers and multiple consumers may all share
the same bounded buffer.
